### 2020-09-20 README.Rmd
Working through the chagens for run_shuffle and run_cv

```{r, eval = run_bw}
# Big Woods
# Read in census data from 2008 & 2014
data(bw_census_2008, bw_census_2014 )

@@

bw_growth_df <-
  # Merge both censuses and compute growth:
  compute_growth(bw_census_2008, bw_census_2014, id) %>%
  mutate(sp = to_any_case(sp)) %>%
  # drop stemID
  select(-stemID)

>>>>

```{r, eval = run_bw}
# Big Woods
# Read in census data from 2008 & 2014
data(bw_census_2008, bw_census_2014, bw_species)

# Append additional species data
bw_census_2008 <- bw_census_2008 %>%
  left_join(bw_species, by = "sp") %>%
  select(-c(genus, species, latin))

@@

bw_growth_df <-
  # Merge both censuses and compute growth:
  compute_growth(bw_census_2008, bw_census_2014, id) %>%
  mutate(
    sp = to_any_case(sp),
    sp = as.factor(sp),
    species = sp,
    family = as.factor(family),
    trait_group = as.factor(trait_group)) %>%
  # drop stemID
  select(-stemID)
